A Theory of Bidirectional Type Synthesis for Simple Types

### 2023-06-25 tex/sec1-intro.tex
[ tex ] Some minor fixes

\begin{remark} \label{re:type-signature}
The majority of existing theories treat types independently of terms, thereby excluding them from binding signatures.
To the best of our knowledge, the only exception to this approach is found in the work of~\citet{Arkor2020}, which incorporates signatures and equations for both terms and types.
Interestingly, this inclusion is critical for type synthesis when comparing a concrete type $N \bto N$ with an abstract type $A \bto B$, where $A$ and $B$ are type variables in a typing rule.
\end{remark}

@@

\paragraph{Type Checker Generation}
While there have been some efforts to generate type checkers grounded in unification~\citep{Gast2004,Grewe2015}, it should be noted that approaches solely based on unification are not suited to handling more complex type theories.

\cite{Pacak2020,Cimini2020}.

>>>>

\begin{remark} \label{re:type-signature}
Most of existing theories treat types independently of terms, thereby excluding them from signatures.
To the best of our knowledge, the only exception to this approach is found in the work of~\citet{Arkor2020}, which incorporates signatures for both terms and types.
Interestingly, this inclusion is critical for type synthesis for comparing a concrete type $N \bto N$ with an abstract type $A \bto B$, where $A$ and $B$ are type variables in a typing rule.
\end{remark}

@@

\paragraph{Type Checker Generation}
While there have been some efforts to generate type checkers grounded in unification~\citep{Gast2004,Grewe2015}, it should be noted that approaches solely based on unification are not suited to handling more complex type theories.
\LT{Check literature \cite{Pacak2020,Cimini2020}.}
